Transience prediction

### 2021-07-27 transience-prediction.tex
addition of conditions

>>>>

\begin{align*}
  y_{i,t} &= \eta_i + \phi_i y_{i,t-1} + \mbf{x}_{i,t} \bs{\beta}_i + \xi_i\cdot  I(t > T_i^*) + \varepsilon_{i,t},\\
  \xi_i &= \alpha_i \cdot e^{-(t-T_i^*-1)} \\
  \alpha_i &= \mu_{\alpha} + \mbf{x}_{i,T_i^*+1}\bs{\gamma}_i + \tilde{\varepsilon}_{i},
\end{align*}

\begin{table}[H]
\caption{50 MC simulations  with varying $n$ and $\sigma_{\alpha}$ ($B = 200$, $H = 12$, $\ell = 3$, $\mu_{\alpha}=10$) \\ MC mean and standard errors for absolute differences between $p_1$ and estimated $p_1$.} \vspace{-.5cm} 
\begin{center}
  \begin{tabular}{cccc}
  $n$ & $\sigma_{\alpha}$ & $|\hat{p}-p_1|$ & $|\hat{I}- I_1|$ \\ 
  \hline
\multirow{5}{*}{5} & 1  & 0.083 (0.028) & 0.084 (0.028) \\ 
    & 5  & 0.083 (0.028) & 0.084 (0.028) \\ 
    & 10  & 0.083 (0.028) & 0.084 (0.028) \\ 
    & 25  & 0.074 (0.027) & 0.074 (0.027) \\ 
    & 100  & 0.053 (0.019) & 0.053 (0.019) \\[.15cm] 
    \hline 
   \multirow{5}{*}{10} & 1  & 0.063 (0.03) & 0.063 (0.03) \\ 
   & 5  & 0.063 (0.03) & 0.063 (0.03) \\ 
   & 10  & 0.063 (0.03) & 0.063 (0.03) \\ 
   & 25  & 0.063 (0.03) & 0.063 (0.03) \\ 
    & 100  & 0.052 (0.025) & 0.052 (0.025) \\[.15cm] 
     \hline 
  \multirow{5}{*}{15} & 1  & 0.065 (0.026) & 0.066 (0.026) \\ 
   & 5  & 0.065 (0.026) & 0.066 (0.026) \\ 
    & 10  & 0.065 (0.026) & 0.066 (0.026) \\ 
   & 25  & 0.065 (0.026) & 0.066 (0.026) \\ 
    & 100  & 0.087 (0.029) & 0.087 (0.029) \\[.15cm]  
     \hline 
   \multirow{5}{*}{25}& 1  & 0.044 (0.021) & 0.044 (0.021) \\ 
    & 5  & 0.043 (0.021) & 0.044 (0.021) \\ 
    & 10  & 0.05 (0.022) & 0.05 (0.022) \\ 
    & 25  & 0.05 (0.022) & 0.05 (0.022) \\ 
    & 100  & 0.048 (0.022) & 0.049 (0.022) \\   
  \end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{100 MC simulations  with varying $\sigma$ and $\sigma_{\alpha}$ ($B = 200$, $H = 12$, $\ell = 3$, $n=10$) \\ MC mean and standard errors for absolute differences between $p_1$ and estimated $p_1$.} 
  \begin{center}
    \begin{tabular}{ccccc}
     $\sigma$ & $\sigma_{\alpha}$ &  $|\hat{p}-p_1|$ & $|\hat{I}- I_1|$ \\[.15cm]  
     \hline 
   \multirow{5}{*}{5}  & 5  & 0.039 (0.016) & 0.04 (0.016) \\ 
     & 10  & 0.039 (0.016) & 0.04 (0.016) \\ 
     & 25  & 0.054 (0.019) & 0.054 (0.019) \\ 
     & 50  & 0.059 (0.019) & 0.059 (0.019) \\ 
     & 100  & 0.098 (0.026) & 0.098 (0.026) \\[.15cm]  
      \hline 
    \multirow{5}{*}{10}  & 5  & 0.044 (0.016) & 0.044 (0.016) \\ 
     & 10  & 0.044 (0.016) & 0.044 (0.016) \\ 
     & 25  & 0.042 (0.016) & 0.042 (0.016) \\ 
     & 50  & 0.065 (0.019) & 0.065 (0.019) \\ 
     & 100  & 0.101 (0.026) & 0.101 (0.026) \\[.15cm]  
      \hline 
    \multirow{5}{*}{25}  & 5  & 0.045 (0.018) & 0.046 (0.018) \\ 
     & 10  & 0.058 (0.02) & 0.059 (0.02) \\ 
     & 25  & 0.06 (0.02) & 0.061 (0.02) \\ 
     & 50  & 0.105 (0.026) & 0.106 (0.026) \\ 
     & 100  & 0.122 (0.027) & 0.122 (0.027) \\[.15cm]  
      \hline 
    \multirow{5}{*}{50}  & 5  & 0.075 (0.023) & 0.076 (0.023) \\ 
     & 10  & 0.085 (0.025) & 0.086 (0.025) \\ 
     & 25  & 0.08 (0.023) & 0.08 (0.023) \\ 
     & 50  & 0.14 (0.029) & 0.14 (0.029) \\ 
     & 100  & 0.148 (0.027) & 0.148 (0.027) \\[.15cm]  
      \hline 
    \multirow{5}{*}{100}  & 5  & 0.148 (0.029) & 0.149 (0.029) \\ 
    & 10  & 0.151 (0.029) & 0.151 (0.029) \\ 
     & 25  & 0.162 (0.029) & 0.162 (0.029) \\ 
     & 50  & 0.229 (0.034) & 0.229 (0.034) \\ 
     & 100  & 0.272 (0.034) & 0.272 (0.034) \\
    \end{tabular}
  \end{center}  
\end{table}

\begin{table}[H]
\caption{100 MC simulations for decaying shock effects with varying $\mu_{\alpha}$ and $H$  ($B = 200$, $\mu_{\gamma}=2$, $\ell = 3$, $n=10$)} 
\begin{center}
\begin{tabular}{rrrccc}
  \hline
 $\mu_{\alpha}$ & $H$ & $|\hat{p}-p_1|$ & $|\hat{I}- I_1|$ & Mean of $p$-values in the donor pool \\ 
  \hline
 0 & 2 & 0.11 (0.023) & 0.114 (0.023) & 0.08 (0.009) \\ 
 5 & 2 & 0.1 (0.021) & 0.1 (0.021) & 0.079 (0.009) \\ 
 50 & 2 & 0.075 (0.018) & 0.075 (0.018) & 0.062 (0.008) \\ 
   100 & 2 & 0.064 (0.017) & 0.064 (0.017) & 0.048 (0.007)  \\[.15cm]  
    \hline 
   0 & 4 & 0.12 (0.025) & 0.124 (0.025) & 0.069 (0.007) \\ 
   5 & 4 & 0.12 (0.025) & 0.12 (0.025) & 0.064 (0.007) \\ 
   50 & 4 & 0.087 (0.022) & 0.094 (0.023) & 0.046 (0.007) \\ 
   100 & 4 & 0.049 (0.016) & 0.049 (0.017) & 0.033 (0.006)  \\[.15cm]  
    \hline 
   0 & 8 & 0.184 (0.031) & 0.192 (0.032) & 0.07 (0.008) \\ 
   5 & 8 & 0.181 (0.032) & 0.191 (0.033) & 0.067 (0.008) \\ 
   50 & 8 & 0.139 (0.029) & 0.139 (0.029) & 0.05 (0.007) \\ 
   100 & 8 & 0.102 (0.024) & 0.103 (0.024) & 0.04 (0.007)  \\[.15cm]   
    \hline 
   0  & 16  & 0.202 (0.031) & 0.202 (0.031) & 0.097 (0.008) \\ 
   5 & 16 & 0.202 (0.031) & 0.202 (0.031) & 0.095 (0.008) \\ 
   50 & 16 & 0.168 (0.031) & 0.168 (0.031) & 0.064 (0.008) \\ 
   100 & 16 & 0.125 (0.029) & 0.125 (0.029) & 0.044 (0.006) \\ 
   \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[H]
\caption{100 MC simulations for decaying shock effects with varying $\ell$ and $H$  ($B = 200$, $\mu_{\gamma}=2$, $\mu_{\alpha}=5$, $n=10$)} 
\begin{center}
\begin{tabular}{rrrccc}
  \hline
  $\ell$ & $H$ &  $|\hat{p}-p_1|$ & $|\hat{I}- I_1|$ & Mean of $p$-values in the donor pool  \\ 
  \hline
 2  &  \multirow{4}{*}{2}  & 0.107 (0.026) & 0.12 (0.028) & 0.064 (0.008) \\ 
   4  &  & 0.108 (0.022) & 0.118 (0.023) & 0.077 (0.008) \\ 
   8  &   & 0.105 (0.024) & 0.107 (0.024) & 0.067 (0.009) \\ 
   16  &   & 0.12 (0.025) & 0.124 (0.026) & 0.07 (0.009) \\[.15cm] 
    \hline  
   2  & \multirow{4}{*}{4}  & 0.162 (0.032) & 0.172 (0.033) & 0.061 (0.008) \\ 
   4  &  & 0.089 (0.017) & 0.097 (0.019) & 0.08 (0.008) \\ 
   8  &   & 0.135 (0.027) & 0.135 (0.027) & 0.08 (0.009) \\
   16  &   & 0.156 (0.031) & 0.158 (0.031) & 0.063 (0.007) \\[.15cm]  
   \hline  
   2  & \multirow{4}{*}{8}  & 0.108 (0.025) & 0.112 (0.025) & 0.079 (0.009) \\ 
   4  &   & 0.134 (0.029) & 0.136 (0.029) & 0.071 (0.008) \\ 
   8  &   & 0.186 (0.033) & 0.186 (0.032) & 0.075 (0.008) \\ 
   16  &   & 0.125 (0.026) & 0.125 (0.026) & 0.071 (0.008) \\[.15cm] 
    \hline  
   2  & \multirow{4}{*}{16}  & 0.222 (0.033) & 0.225 (0.033) & 0.094 (0.01) \\ 
   4  &   & 0.124 (0.024) & 0.126 (0.024) & 0.081 (0.008) \\ 
   8  &   & 0.14 (0.028) & 0.14 (0.028) & 0.075 (0.008) \\ 
   16  &   & 0.162 (0.032) & 0.162 (0.032) & 0.068 (0.009) \\ 
   \hline
\end{tabular}
\end{center}
\end{table}

\section{Conditions}

\begin{enumerate}
  \item Donor pool sample size $n \to \infty$
  \item $\|\alpha_1 - \hat{\alpha}_{w} \|_2 \to 0$ as $n\to \infty$ (this can be realized by setting $\sigma_{\alpha}$ small enough and $\Var(\bs{\gamma} )$ small enough)
  \item The set of weights that are positive is fixed and finite asymptotically 
  \item Conditions of Quaedvlieg and $B \to \infty$
  \item $T_i \to \infty$ for $i = 2,\ldots, n+1$ and $T_i^* =o(T_i)$.
\end{enumerate}

If all those conditions hold, $\| p_1-\hat{p}\| \to 0$.
